First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-29 ms.tex
Fixed details of residual flux density cut re: Pattis email

Our final data cut was made when inspecting the residual continuum images output from 
FHD. We test for residual brightness at source locations by calculating a fractional residual brightness RMS 
in the following way. For each snapshot 
continuum image, we find the residual brightness in the pixels of all sources greater than 0.5 Jy 
subtracted within half-beam power and scale by the integrated flux density of the sources. This 
gives us a list of fractional residual brightnesses for the snapshot, which we then use to calculate 
an RMS. We found that most snapshots had residual brightness RMS $<10\%$ with some outliers, 
which we cut from the data. This cut largely overlapped with previous cuts, but removed an 
additional 95 observations. The cause of the high residual brightness RMS is yet unknown and is 
not localized by observation day, LST, pointing, or any other jackknife we have performed.

>>>>

Our final data cut was made when inspecting the residual continuum images output from 
FHD. We test for residual flux density at source locations by calculating a fractional residual flux density RMS 
in the following way. For each snapshot 
continuum image, we find the residual flux density of all sources greater than 0.5 Jy 
subtracted within half-beam power by integrating the brightness within the source pixel.
We then scale by the integrated flux density of the sources, giving us a list of fractional
residual flux densities for the snapshot, which we then use to calculate an RMS. We found
that most snapshots had residual flux density RMS $<10\%$ with some outliers,
which we cut from the data. This cut largely overlapped with previous cuts, but removed an 
additional 95 observations. The cause of the high residual flux density RMS is yet unknown and is 
not localized by observation day, LST, pointing, or any other jackknife we have performed.
